### 2017-10-23 paper/sections/1_introduction.tex
paper: fix some typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% What is the problem?
File system metadata services in HPC and data center applications  have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current hardware and software trends; for example, HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

@@

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the semantics and their performance is explored
in~\S\ref{sec:use-case-1}.} subtree has weaker than strong consistency because
for performance it lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all servers; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.

>>>>

% What is the problem?
File system metadata services in HPC and large-scale data centers have
scalability problems because common tasks, like
checkpointing~\cite{bent_plfs_2009} or scanning the file
system~\cite{zheng:pdsw2014-batchfs}, contend for the same directories and
inodes. Applications perform better with dedicated metadata
servers~\cite{sevilla:sc15-mantle, ren:sc2014-indexfs} but provisioning a
metadata server for every client is unreasonable. This problem is exacerbated
by current hardware and software trends; for example, HPC architectures are
transitioning from complex storage stacks with burst buffer, file system,
object store, and tape tiers to more simplified stacks with just a burst buffer
and object store~\cite{bent:login16-hpc-trends}. These types of trends put
pressure on data access because more requests end up hitting the same layer and
latencies cannot be hidden while data migrates across tiers.

@@

% What did we do
To address this problem, we present an API and framework that lets developers
dynamically control the consistency and durability guarantees for subtrees in
the file system namespace.  Figure~\ref{fig:subtree-policies} shows a potential
setup in our proposed system where a single global namespace has subtrees for
applications optimized with techniques from different state-of-the-art
architectures.  The HDFS\footnote{HDFS itself is not directly evaluated in this
paper, although the semantics and their performance is explored
in~\S\ref{sec:use-case-1}.} subtree has weaker than strong consistency because
it lets clients read files opened for
writing~\cite{hakimzadeh:dais14-hdfs-consistency}, which means that not all
updates are immediately seen by all clients; the BatchFS and RAMDisk subtrees
are decoupled from the global namespace and have similar consistency/durability
behavior to those systems; and the POSIX IO subtree retains the rigidity of
POSIX IO's strong consistency.  Subtrees without policies inherit the
consistency/durability semantics of the parent and future work will examine
embeddable or inheritable policies.
